\documentclass[a4paper]{article}
\input{../../common/Packages.tex}
\makenoidxglossaries

\title{{\em The FLOSSary}:\\
  A Glossary af Free and Open Source Software related Terminology}

\author{TheFLOSSary Contributors\\
  \\
  Editor: Mirko Boehm\\
  Chair of Innovation Economics\\
  Technical University of Berlin\\
  \texttt{mirko@fsfe.org}}

\date{\today}

\input{../../Data/Glossary-FOSS}
\begin{document}
\newcommand{\flossary}{{\em FLOSSary} }

\maketitle \thispagestyle{empty}
\begin{abstract}
  \noindent
  The \flossary is a free glossary of terms and definitions related to
  \gls{FLOSS}. It serves as a point of reference for the participants
  in the ``Open Source and Intellectual Property in the Digital
  Society'' the the Technical University of Berlin, and may be reused
  in other contexts like papers or presentations.

  The \flossary is
  collectively edited by the participants and tutors of the course and
  distributed freely under the conditions of the CC BY 4.0 license.
\end{abstract}

\begin{flushleft}
{\bf Peer review:} 
In software development, peer review is a type of software review in which a work product (document, code, or other) is examined by its author and one or more colleagues, in order to evaluate its technical content and quality. \bigskip

In OSS, We extract a series of measures based on those used in traditional inspection experiments. We measure the frequency of review, the size of the contribution under review, the level of participation during review, the experience and expertise of the individuals involved in the review, the review interval, and the number of issues discussed during review. We create statistical models of the review efficiency, review interval, and effectiveness, the issues discussed during review, to determine which measures have the largest impact on review efficacy. We find that OSS peer reviews are conducted asynchronously by empowered experts who focus on changes that are in their area of expertise. Reviewers provide timely, regular feedback on small changes. The descriptive statistics clearly show that OSS review is drastically different from traditional inspection. 
\end{flushleft}


\clearpage
\glsaddall
\printnoidxglossary[nonumberlist]
\clearpage
\printnoidxglossary[type=\acronymtype,nonumberlist]
\clearpage
\bibliography{../../Data/Bibliography}
\end{document}

