% Terms that need definition:
%
% (Students: You *cannot* use these terms before they have been referenced in the course! :-)
% license compliance
% license compatibility,
% inbound/outbound license
% governance
% four freedoms of software
% share-alike/reciprocal/copyleft/permissive/academic
% viral effect
% FLOSS/FOSS/OSS
% tivoization
% freedom to operate (ability to exercise 4 freedoms and to pursue own interest)
% automatic licensing
% transitive licensing
% non-negotiable licensing
% enforcement of licensing terms
% peer production

\newacronym[see={fsry:FOSS}]{fsry:FLOSS}{FLOSS}{free/libre and open source software}
\newacronym[see={fsry:FOSS}]{fsry:OSS}{OSS}{open source software}
\newacronym{fsry:GA}{GA}{general assembly}
\newacronym{fsry:ODF}{OpenDocument}{Open Document Format for Office Applications}
\newacronym{fsry:WIPO}{WIPO}{World Intellectual Property Organization}
\newacronym{fsry:TAC}{TAC}{transaction cost}

\dualfsryentry{FOSS}{FOSS}{free and open source software}{The term
  free and open source software refers to software that is distributed
  under a license which complies with the \gls{fsry:OSD} or
  respectively the definition of \gls{fsry:FS} provided by the
  \gls{fsry:FSF}. The \gls{fsry:OSI} is the steward that approves
  licenses for being compliant with the \gls{fsry:OSD}.  Free and open
  source software is made available to everybody under a license that
  gives the user the freedom to run, copy, distribute, study, change
  and improve the software. ``'free software' is a matter of liberty,
  not price''.\cite{fsry:RMS-essays-2010} The \gls{fsry:FSF} and the
  \gls{fsry:OSI} maintain lists of
  licenses\footnote{\url{https://www.gnu.org/licenses/license-list.html},
    \url{https://opensource.org/licenses}} that provide at least those
  ``four essential freedoms'' to recipients of the software. The terms
  of all licenses that provide these terms turn the product into a
  \gls{fsry:pubgood} and also ensure that the product itself will
  continue to be freely licensed. This effect may or may not extend to
  derivative works and future versions, resulting in the
  classification of the licenses into reciprocal and permissive
  categories.  }

\newglossaryentry{fsry:FS}{name={free software}, description={}, see={fsry:FOSS}}

\dualfsryentry{FSFE}{FSFE}{Free Software Foundation Europe}{The Free
  Software Foundation Europe ``is a charity that empowers users to
  control
  technology''.\footnote{\url{https://fsfe.org/about/about.en.html}}}

\newglossaryentry{fsry:KDE}{name={KDE}, description={KDE is a recursive
    acronym that refers to the ``K Desktop Environment'', a graphical
    computing environment for \gls{fsry:FOSS} operating systems. It is
    produced by the KDE community\footnote{\url{https://www.kde.org}},
    a global, volunteer driven and decentralized \gls{fsry:FOSS} community}.
}

\newglossaryentry{fsry:governance}{name={governance}, description={In the
    context of \gls{fsry:FOSS}, governance describes the totality of
    implicit and explicit behavioral norms, codes and processes that
    regulate the relationship between contributors and the community
    as a whole.} }

\newglossaryentry{fsry:CoC}{name={code of conduct}, description={A
    code of conduct describes the behavioral norms and rules that
    community contributors are expected to adhere to. Once adopted, a
    written code of conduct is part of the explicit
    \gls{fsry:governance} norms of a community.} }

\newglossaryentry{fsry:osw}{name={open source way}, description={The
    colloquial term ``the open source way'' describes the mutual
    understanding of \gls{fsry:SF}, values and principles applied by the
    \gls{fsry:WOSC}, especially the norms of non-negotiable \gls{fsry:FOSS}
    licenses, open governance and \gls{fsry:meritocracy}.}}

\newglossaryentry{fsry:meritocracy}{name={meritocracy}, description={In the
    context of \gls{fsry:FOSS}, the term meritocracy is used to describe a
    system where contributors gain reputation in a community solely
    based on the value of the contributions they make.} }

\newglossaryentry{fsry:WOSC}{name={wider Open Source community}, description={The
  phrase \emph{wider Open Source community} is commonly used to describe the
  totality of individuals, smaller and larger communities, umbrella
  organizations and entities collaborating on developing the commons of
  \gls{fsry:FOSS} in the global \gls{fsry:UDM}.} }

\newglossaryentry{fsry:OSC}{name={community}, plural={communities},
  description={A \gls{fsry:FOSS} community consists of the network of
    participants that contribute to the creation of specific
    \gls{fsry:FOSS} software products, predominantly computer
    programs, in a collaborative peer productions process based on
    voluntary participation. Communities may be set up implicitly or
    explicitly as unincorporated associations, as for-profit or
    not-for-profit legal entities or under \gls{fsry:FOSS}
    \glspl{fsry:umbrellaorg}.}  }

\newglossaryentry{fsry:open-source-culture}{
  name={open source culture},
  description={A synonym for the \gls{fsry:osw}.}
}

\newglossaryentry{fsry:LD}{ name={Linux distribution}, description={A Linux
    distribution is a software collection based on Linux that aggregates the
    work of the \gls{fsry:WOSC} into a complete operating system. Linux distributions
    are an integral part of the \gls{fsry:UDM} because they make \gls{fsry:FS} accessible
    to specific applications like end-user desktops or embedded systems.} }

\newglossaryentry{fsry:UDM}{name={upstream/downstream model}, description={The
  analogy of the upstream/downstream model uses the mental image of a large
  river that collects the water from many smaller and smaller tributaries (the
  communities) and delivers it to the ocean (the users). Key tenets of the
  upstream/downstream model are the non-negotiability of the \gls{fsry:FS} licensing
  terms and community governance norms.} }

\newglossaryentry{fsry:LF}{ name={Linux Foundation}, description={The Linux
    Foundation is a not-for-profit industry association (US 501(c)(6)) dedicated
    to building sustainable ecosystems around open source projects to accelerate
    technology development and commercial adoption.}}

\newglossaryentry{fsry:CWG}{name={community working group},
  description={The community working group of KDE is the only formal
    conflict resolution mechanism the KDE community has in place. ``The
    long-term goal of the Community Working Group is to help to
    maintain a friendly and welcoming KDE community, thereby ensuring
    KDE remains a great project enjoyed by all contributors and
    users.''\footnote{\url{https://ev.kde.org/workinggroups/cwg.php}} } }

\newglossaryentry{fsry:EF}{ name={Eclipse Foundation}, description={The Eclipse
    Foundation is a not-for-profit industry association (US 501(c)(6)) that
    provides a global community of individuals and organizations with a mature,
    scalable, and commercially focused environment for collaboration and
    innovation.} }

\newglossaryentry{fsry:eV}{name={KDE~e.V.}, description={KDE
    e.V.\footnote{\url{https://ev.kde.org/}} is a non-profit organization
    registered in Berlin, Germany that represents the KDE Community in
    legal and financial matters.} }

\newglossaryentry{fsry:FSF}{name={FSF}, description={``The Free Software
    Foundation (FSF) is a nonprofit with a worldwide mission to
    promote computer user freedom.''\footnote{\url{http://www.fsf.org/}}} }

\newglossaryentry{fsry:FTF}{name={Freedom Task Force}, description={The
    {\em Freedom Task Force} is an intiative of \gls{fsry:FSFE} that
    ``seeks to help programmers properly set up and organise projects
    legally, as well as educate companies to understand how the GPL
    works.  As needed, the purpose of the group will also include
    enforcement in the case of licence
    violations.''\footnote{\url{http://mail.fsfeurope.org/pipermail/press-release/2006q4/000159.html}}
    The Freedom Task Force was created in 2006.} }

\newglossaryentry{fsry:LN}{name={Legal Network}, description={The
    \gls{fsry:FSFE} {\em Legal Network}, initially called the European
    Legal Network, is a ``neutral, non-partisan, group of experts in
    different fields involved in Free Software legal issues. Currently
    the Legal Network has over 400 participants from different legal
    systems, academic backgrounds and
    affiliations''.\footnote{\url{https://fsfe.org/activities/ftf/ln.en.html}}
} }

\newglossaryentry{fsry:OS}{name={open source}, description={The term
    ``open source'' is used in this paper and many other contexts as a
    synonym to \gls{fsry:FOSS}. It originally describes a campaign to
    promote \gls{fsry:FS} to
    business.\cite{fsry:perens-open-source-2017}}, see={fsry:FOSS} }

\newglossaryentry{fsry:OSI}{name={Open Source Initiative}, description={The
    Open Source Initiative\footnote{\url{https://opensource.org}} was
    founded in 1998 by Eric Raymond and Bruce Perens. It is dedicated
    to the promotion of open source software. The term ``open source''
    was coined by the initiative's founders. It created the initial
    \gls{fsry:OSD}. Today the Open Source Initiative is the steward
    of the Open Source Definition (OSD) and the
    community-recognized body for reviewing and approving licenses as
    OSD-conformant. It publishes the list of all approved open source
    licenses.\footnote{\url{https://opensource.org/licenses/alphabetical}}
    The The Open Source Initiative is a California public benefit
    corporation, with 501(c)3 tax-exempt status.} }

\newglossaryentry{fsry:OSD}{name={Open Source Definition}, description={The Open
    Source Definition formulates the terms software must comply with to be
    considered \gls{fsry:FOSS}.\footnote{\url{https://opensource.org/osd}} It is
    maintained by the \gls{fsry:OSI}. By way of the Open Source Definition,
    especially it's unanimous acceptance, the term ``open source'' gained a
    precise meaning across the \gls{fsry:WOSC}, and is therefore a
    term of art and part of open source culture.}, see={fsry:FOSS}}

\newglossaryentry{fsry:SF}{name={software freedom},
  description={``Software freedom'' is what distributing a work under
    a \gls{fsry:FOSS} license affords the user. While the terms
    \gls{fsry:FS} and \gls{fsry:OS} are used mostly synonymously
    today, ``software freedom'' is a political goal elements of the
    \gls{fsry:FS} movement aim for. It can be circumscribed as the
    absence of coercion to use proprietary
    software.\cite{fsry:RMS-essays-2010} Organisations like the
    Software Freedom
    Conservancy\footnote{\url{https://sfconservancy.org/}} and the
    Software Freedom Law
    Center\footnote{\url{https://www.softwarefreedom.org/}} work to
    advance software freedom.} }

\newglossaryentry{fsry:WM}{name={Wikimedia}, description={Wikimedia is the
    global community that creates \gls{fsry:WP}.}}

\newglossaryentry{fsry:WMF}{name={Wikimedia Foundation}, description={The
    Wikimedia Foundation is a US-based non-profit
    organisation that represents Wikipedia globally.} }

\newglossaryentry{fsry:WMDE}{name={Wikimedia Deutschland e.V.},
  description={Wikimedia Deutschland e.V.  is a non-profit
    organization registered in Berlin, Germany that represents the
    German language Wikipedia community.} }

\newglossaryentry{fsry:WP}{name={Wikipedia}, description={Wikipedia is an
    online encyclopedia that aims at making the knowledge of the world
    available to everybody.} }

\newglossaryentry{fsry:VS}{name={versioning}, description={Versioning of
    software is the unique naming of software identifying it's development.
    For example, version 1.0 is commonly used to identify a first edition.} }

\newglossaryentry{fsry:DSC}{name={Debian Social Contract},
  description={``Debian Social Contract'' refers to the Debian
    developers' commitment towards the \gls{fsry:FS} community. The Debian
    Social Contract is a 'moral agenda' which is based on the Debian
    Free Software Guidelines according to which Debian promises to be
    entirely free, provide the best work, not try to cover problems,
    give priority to users and free software and to make it possible
    for the software to be used with non-free software. The
    commitments of the Debian Social Contract have later been adopted
    into the
    \gls{fsry:OSD}.\footnote{\url{https://www.debian.org/social_contract}} }
}

\dualfsryentry{DRM}{DRM}{Digital Rights Management}{ A collection
  of technologies that can be used to protect the copyright of
  electronic media including software and multimedia content. The way
  it is done mostly includes restricting the use of hardware and
  copyrighted works.  For example, certain multimedia companies can
  restrict the number of devices the media can be played on or force
  customers to use a specific application / device to play the
  contents of the desired
  media.\cite{fsry:ec-council-2009}\footnote{\url{https://www.eff.org/issues/drm}}
}

%%% Removed as not FOSS related:
%% \newglossaryentry{fsry:RE}{name={Reverse Engineering}, description={Reverse
%%     engineering is taking apart an object to see how it works in order
%%     to duplicate or enhance the object.  The practice, taken from
%%     older industries, is now frequently used on computer hardware and
%%     software. Software reverse engineering involves reversing a
%%     program's machine code (the string of 0s and 1s that are sent to
%%     the logic processor) back into the source code that it was written
%%     in, using program language statements.
%% \footnote{\url{https://en.wikipedia.org/wiki/Reverse_engineering}}
%% \footnote{\url{https://searchsoftwarequality.techtarget.com/definition/reverse-engineering}}
%% } }

\newglossaryentry{fsry:GIT}{name={Git}, description={Git is open source
    software used for distributed versioning of files.  It was
    invented in 2005 by Linus Torvald, who is also the creator of the
    Linux kernel.} }

\newglossaryentry{fsry:SC}{name={source code}, description={Source code is
    the fundamental component of a computer program that is created by
    a programmer and is referred to as the "before" versions of a
    compiled computer
    program.\footnote{\url{https://searchmicroservices.techtarget.com/definition/source-code}}
} }

%%% Commented because the description is incorrect:
%% \newglossaryentry{fsry:CM}{name={committer}, description={Committers are
%%     the community's quality control experts. Somebody has to control
%%     the process.  Committers actually decide what changes, based on
%%     community experience, make it into the originally licensed
%%     program.  A committer is an individual who is able to modify the
%%     source code of a particular piece of open-source software.
%%    \footnote{\url{https://www.techrepublic.com/blog/10-things/10-terms-and-concepts-related-to-open-source/}}
%%  }
%% }

\newglossaryentry{fsry:CND}{name={continuous-non-differentiating
    cooperation}, description={Continuous-non-differentiating
    cooperation is a collaboration model implemented in \gls{fsry:FOSS}
    communities and facilitated by \gls{fsry:FOSS} foundations that enables
    otherwise competing market actors to continuously cooperate to
    develop a common software stack that serves as basic,
    non-differentiating technology prerequisite to products that
    combine free and proprietary software. In contrast to
    pre-competitive cooperation on the development of proprietary,
    differentiating products, anti-trust concerns are not relevant in
    the continous-non-differentiating cooperation model since
    collusion is impossible if the results are immediately available
    to the general public and the development process is generally
    open for participation to all interested parties. The possibility
    of forks limits the control individual entities can exercise over
    the development process.} }

\newglossaryentry{fsry:ICT}{name={ICT}, description={``Information and
    communication technology'' describes the computing and
    telecommunications industry sector. The sector serves the
    information processing, storage and networking demand of the
    digital economy.} }

\newglossaryentry{fsry:OI}{name={open innovation}, description={A business
    concept which encourages companies to acquire outside sources of
    innovation in order to improve product lines and shorten the time
    required to bring products to market or to release internally
    developed
    innovation.\footnote{\url{http://www.businessdictionary.com/definition/open-innovation.html}}
} }

\newglossaryentry{fsry:physicalgoods}{name={physical goods},
  description={Physical goods require at least a combination of labor
    and materials to build. Assuming marginal cost pricing, the price
    of a physical good is affected by the factors required for its
    production, and therefore larger than zero.} }

\newglossaryentry{fsry:information-good}{name={information good},
  description={Information goods are expensive to create, but only
    incur negligible cost of reproduction. Assuming marginal cost
    pricing, the price of an information good converges to zero under
    perfect competition.\cite{fsry:varian-1995} } }

\newglossaryentry{fsry:commodity}{name={commodity}, description={A
    commodity is a good with normalized attributes, giving instances
    of it fungibility. Commodities commonly are produced under price
    competition. \gls{fsry:FOSS} that implements common,
    non-differentiating features of a computer system is considered a
    commodity.} }

\newglossaryentry{fsry:peer review}{name={peer review}, description={In
    software development, peer review is a type of software review in
    which a work product (document, code, or other) is examined by its
    author and one or more colleagues, in order to evaluate its
    technical content and quality.} }

\newglossaryentry{fsry:reciprocal}{name={reciprocal public license},
  description={The Reciprocal Public License is a copyleft software
    license that is based on the concept of reciprocity. In exchange
    for being granted certain rights under the terms of this license
    to the licensor's Software, whose source code you have access to,
    you are required to reciprocate by providing equal access and
    rights to all third parties to the source code of any
    modifications.} }

\dualfsryentry{DMCA}{DMCA}{Digital Millennium Copyright Act}{ The
  Digital Millennium Copyright Act is a 1998 United States copyright
  law that implements two 1996 treaties of the \acrfull{fsry:WIPO}. It
  criminalizes production and dissemination of technology, devices, or
  services intended to circumvent measures that control access to
  copyrighted works (commonly known as \gls{fsry:DRM}). It also
  criminalizes the act of circumventing an access control system,
  whether or not there is actual infringement of copyright itself. In
  addition, the DMCA heightens the penalties for copyright
  infringement on the Internet.  Passed on October 12, 1998, by a
  unanimous vote in the United States Senate and signed into law by
  President Bill Clinton on October 28, 1998, the DMCA amended Title
  17 of the United States Code to extend the reach of copyright, while
  limiting the liability of the providers of online services for
  copyright infringement by their users.\cite{fsry:dmca-wiki,
    fsry:dmca-overview}}

\newglossaryentry{fsry:copyleft}{name={copyleft}, description={ A general method for
    making a program (or other work) free (in the sense of freedom, not ''zero
    price''), and requiring all modified and extended versions of the program to be
    free as well.\cite{fsry:gnu-copyleft}} }

\newglossaryentry{fsry:CSS}{name={Content Scramble System}, description={An
    early \gls{fsry:DRM} scheme designed for the protection of the contents
    of a commercially produced DVD video disc.  The circumvention of
    this copy protection scheme by the usage of the program
    \texttt{DeCSS} was the subject of one of the earliest legal cases
    involving the distribution of software that can circumvent copy
    protection code.} }

\newglossaryentry{fsry:impodispossess}{name={impossibility to dispossess},
  description={In the context of intellectual property, after an idea
    or knowledge is transferred, it is impossible to force the
    receiver to forget it or to dispossess it. The process of
    knowledge transfer cannot be reversed.\cite{fsry:digirightmana}} }

\newglossaryentry{fsry:contribuagree}{name={contribution agreement},
  description={In the \gls{fsry:FOSS} context, a contribution
    agreement covers the relationship between the community and a
    contributor. It is a legal document that specifies the conditions
    for licensing or transferring the rights of using, reproducing,
    modifying, and distributing a product from the contributor to
    another entity, like a community organization or a business
    dominating the development process.\cite{fsry:civiccommons}
    Contribution agreements vary widely in their terms. They may
    create asymmetry between contributors, which is considered a
    violation of \gls{fsry:open-source-culture} by some authors. In
    most cases, the author retains copyright ownership, but grants
    perpetual, worldwide, irrevocable and no-charge rights over his or
    her work to a business or foundation.\cite{fsry:hammouda-2012}}}

\newglossaryentry{fsry:BDFL}{name={BDFL}, description={Short for
    Benevolent Dictator For Life. BDFLs are rare in \gls{fsry:FOSS}
    but they do exist. For example, Guido van Rossum was the BDFL of
    Python and Dries Buytaert is the BDFL of Drupal. A BDFL is
    typically the founder of the project. They have final say in and
    can veto all decisions related to the project, but it’s very rare
    that they use this power. Typically a BDFL will lean on the
    Benevolent part of the title by seeking consensus and always
    working toward what’s best for both the project and its
    community.\cite{fsry:brasseur-2018}} }

\newglossaryentry{fsry:Modularity}{name=Modularity, description={Modularity
    is a property of a project referring to the extent to which it can
    be broken down into smaller components, or modules, that can be
    independently and asynchronously produced before they are
    assembled into a whole. If modules are independent, individual
    contributors can choose what and when to contribute independently
    of each other, thereby maximizing their autonomy and flexibility
    to define the nature, extent, and timing of their participation in
    the project. Given the centrality of self-direction of human
    creative effort to the efficiencies of peer production, this
    characteristic is salient.\cite{fsry:benkler-2002}} }

\newglossaryentry{fsry:Granularity}{name=Granularity,
  description={Granularity refers to the size of the modules, in terms
    of the time and effort that an agent must invest in producing
    them. The number of people who will likely participate in a
    project is inversely related to the size of the smallest-scale
    contribution necessary to produce a usable module. Usability may
    place a lower boundary on granularity either for technical or
    economic reasons, where at a minimum the cost of integrating a
    component into a larger modular project must be lower than the
    value that adding that component adds to the project. But above
    that boundary, the granularity of the modules sets the smallest
    possible individual investment necessary to participate in a
    project. If this investment is sufficiently low, then incentives
    for producing that component of a modular project can be of
    trivial magnitude and many people can contribute. If the
    finest-grained contributions are relatively large and would
    require large investment of time and effort, the universe of
    potential contributors decreases. A successful large-scale peer
    production project must therefore have a predominate portion of
    its modules be relatively fine-grained. The discussion in the
    preceding section suggests that, given the relatively small
    independent value such fine-grained contributions will have and
    the transaction costs associated with remunerating each
    contribution monetarily, non-monetary reward structures are likely
    to be more effective to motivate peer production
    efforts.\cite{fsry:benkler-2002}} }

\newglossaryentry{fsry:joint-authorship}{name={joint authorship},
  description={Participants create works under joint authorship if
    they contribute under the intention that their separate
    contributions be merged into a single work. Absent other
    agreements, each author may grant permission to use of the work
    separately. Depending on the \gls{fsry:OSC} collaboration model,
    \gls{fsry:FOSS} contributors often intend to create a single source
    code package from many individual contributions, potentially
    leading to joint authorship.\cite{fsry:usc-joint-authorship}} }

\newglossaryentry{fsry:software-stack}{name={Software Stack},
  description={A software stack can have the following meanings
    \cite{fsry:technopedia-software-stack, fsry:wiki-software-stack}:
    \begin{itemize}
    \item A group of programs that work together to produce a
      result or achieve a common goal.
    \item Any set of applications that works in a specific and
      defined order toward a common goal. For example for the
      Linux-based software stack is LAMP (Linux, Apache, MYSQL,
      Perl or PHP or Python) for developing web services.
    \item The set of applications or programming languages used by
      team to developed solutions/projects
    \end{itemize}
} }

\newglossaryentry{fsry:opencore}{name={Open Core}, description={ The
    open-core model is a business model for the monetization of
    commercially-produced open-source software. It involves primarily
    offering a "core" or feature-limited version of a software product
    as free and open-source software, while offering "commercial"
    versions or add-ons as proprietary software.\cite{fsry:wiki-opencore}}}

\newglossaryentry{fsry:OSHW} { name = {Open Source Hardware}, description = {
    "Open hardware," or "open source hardware," refers to the design
    specifications of a physical object which are licensed in such a way
    that said object can be studied, modified, created, and distributed by
    anyone.\cite{fsry:open-hardware} } }

\newglossaryentry{fsry:pubgood}{name={public good}, description={A public
    good is a good that is both non-excludable and non-rivalrous. The
    application of a \gls{fsry:FOSS} license makes software source code a
    public good.} }

\newglossaryentry{fsry:umbrellaorg} { name = {umbrella organization},
  description = {An umbrella organization hosts individual projects
    within a single administrative structure. The \gls{fsry:EF}, the
    \gls{fsry:LF} and \gls{fsry:eV} are examples for umbrella organizations for
    \gls{fsry:FOSS} projects} }

\newglossaryentry{fsry:fork} { name = {fork}, description = {A fork is
    a split of the development of a \gls{fsry:FOSS} product into two
    new communities. Forks introduce duplication of efforts and other
    downsides and are usually avoided unless there is strong
    disagreement over community governance. Prominent forks are
    LibreOffice (forked from OpenOffice), MariaDB (forked from or)
    MySQL or Nextcloud (forked from ownCloud). The term fork is
    sometimes also used in the sense of branches for experimental
    development efforts or on Github for a copy of a repository.} }

\newglossaryentry{fsry:commcomp} { name = {community composition},
  description = {Community composition describes how the contributors
    to a community are comprised of individual volunteers,
    organisations, employed staff and other constituencies. It is
    assumed that community composition influences governance
    norms. Hybrid communities composed of a mix of businesses,
    individual volunteers and possibly staff are most common. } }

\newglossaryentry{fsry:bikeshedding} { name = {bike-shedding},
  description = {Bike-shedding describes the habit of bringing up
    tangential arguments in a debate that distract from the issue at
    hand. It is named after the question of which colour to paint the
    bike shed when the debate is about whether or not to build
    one. The use of the term in the \gls{fsry:WOSC} originated in the
    BSD community in 1999. It is popular in \gls{fsry:KDE} and
    many other communities.}}

\newglossaryentry{fsry:rivalrous} { name = {rivalrous}, description =
  {A good is rivalrous if its consumption by one consumer prevents or
    inhibits simultaneous consumption by other consumers. Most
    physical goods are rivalrous, while most information goods are
    non-rivalrous.}}

\newglossaryentry{fsry:excludable} { name = {excludable}, description
  = {A good is excludable if access to it can be controlled so that a
    person can be prevented from consuming it. \gls{fsry:FOSS}
    licences make software a non-excludable good.}}

\newglossaryentry{fsry:gearykhamisindex} { name = {Geary-Khamis Index}, description
    = {Short: The Geary-Khamis index compares countries GDP by converting
    their local currencies into Geary-Khamis Dollars using the Geary-Khamis method described below. Detailed: ``The Geary-Khamis method is an average price method first used by the ICP to compute PPPs [purchasing power parties]
    and real final expenditures above the basic heading.''\cite{fsry:oecd-geary-khamis-2007} Therefore ``the G-K method yields a vector of international prices and a vector of PPPs such that the international price for an individual good is a weighted average of relative prices in individual countries.
    Each country has a weight corresponding to its share in the GDP of the group /for each of the basic headings/.
    ''\cite{fsry:sensitivity-ppp}}}

\newglossaryentry{fsry:LCM} { name = {liberal contribution model},
  description = { Under a liberal contribution model, the people who
    do the most work are recognized as most influential, but this is
    based on current work and not historic contributions.  Major
    project decisions are made based on a consensus seeking process
    (discuss major grievances) rather than pure vote, and strive to
    include as many community perspectives as possible.  Popular
    examples of projects that use a liberal contribution model include
    Node.js and
    Rust.\cite{fsry:open-source-guides-leadership-governance}}}

\newglossaryentry{fsry:creativework} { name = {Creative Work}, description =
  {``Creative work'' is a term used in the context of copyright law. It describes
  the result of a person's efforts of imagination and may therefore be
  categorized into the following broad topics: artwork, literature,
  music, paintings, and software.}}

\newglossaryentry{fsry:BC}{name={Berne Convention for the Protection of Literary and Artistic Works},
  description={The Berne Convention for the Protection of Literary and Artistic Works is an International agreement
  governing copyright \cite{fsry:wikibc}, \cite{fsry:wipofbc}. It was originally adopted in 1886 and amended in 1979 \cite{fsry:wipobc}.
  The 3 central aspects are:
  \begin{itemize}
  \item principle of „national treatment“: grant foreign works the same protection as
  for own works \cite{fsry:wiposbc}, \cite{fsry:wikibc}
  \item principle of „automatic“ protection: no formal registration required \cite{fsry:wiposbc}, \cite{fsry:wikibc}
  \item principle of „indepedence“ of protection: grant own standard, even if it‘s more
  than in the country of origin (duration is exception) \cite{fsry:wiposbc}
  \end{itemize}
  Based on these three principles and a series of provisions it is defining a minimum protection
  to be granted in every country which signed the Convention. The Convention was also included
  in the Universal Copyright Convention and is almost completly incorporated (with the exception
  of moral rights) in the Agreement on Trade-Related Aspects of Intellectual Property Right(TRIPS)\cite{fsry:wikitrips}.
} }

\newglossaryentry{fsry:creativedestruction} { name = {Creative destruction}, description =
  {A process where a new innovation brings an end to one or more existing ones.} }

\newglossaryentry{fsry:gardenleave} { name = {Garden Leave}, description =
{The purpose of a Garden Leave is to keep the damage of an employee leaving the company as low as possible by keeping them away from clients, colleagues and confidential information \cite{fsry:gardenleave1}. It is also possible to prevent the employee from going to a competitor or starting their own business. During the Garden Leave period the employee usually works from home and remains salary payments. It is recommended to have a gardening leave clause in the contract to ensure clarity for both parties. } }

\newglossaryentry{fsry:Trademarks} { name = {Trademarks}, description
 = {Trademarks are used to identify a product, service or organisation, 
    like a name, symbol or a combination of these. They identify the 
    source of goods or services and are used to distinguish them from 
    goods or services by other parties. Trademarks are defined per class 
    of good. Trademarks can be registered, unregistered or “service 
    marks”. They begin existing with use and can last forever as long 
    they are actively used. Trademarks can become generic terms and 
    loose protection.}}
